Fundamental Problems with the Evidence Base of Adolescent Depression Treatments

### 2024-03-25 Untitled.qmd
Response rate calcualtion

---
title: "Fundamental Problems with the Evidence Base of Adolescent Depression Treatments"
author: "Stringaris et al"
output:
  quarto::pdf_document:
    pandoc_args: --pdf-engine=pdflatex
---

@@

@@

#list_df_simulated[[10]][,c("new_study_id", "correlation_sim_values", "simulated_se")] # looks right
#summary(list_df_simulated[[1000]]$correlation_sim_values, na.rm = T) # as expected # the mean is around the parameter I gave

@@

>>>>

---
title: "Fundamental Problems with the Evidence Base of Adolescent Depression Treatments"
author: "Stringaris et al"
prefer-html: true
format: docx
editor: visual
---

@@

# For response rate, recalculating after turning long and doing all the imputations

# df_long_for_metan <- df_long_for_metan %>%
#   rowwise() %>%
#   mutate(responders = sum(rnorm(baseline_n, post_mean, 
#                                 post_sd) < (baseline_mean/ 2)))
# 
# df_long_for_metan <- df_long_for_metan %>%
#   rowwise() %>%
#   mutate(resp_rate = responders/baseline_n)
# 
# summary_resp_rate <- df_long_for_metan %>%
#   group_by(group) %>%
#   summarise(mean_resp_rate = mean(resp_rate, na.rm = TRUE),
#             sd_resp_rate = sd(resp_rate, na.rm = TRUE), 
#             n = n())

@@

#list_df_simulated[[10]][,c("new_study_id", "correlation_sim_values", "simulated_se")] # looks right
#summary(list_df_simulated[[1000]]$correlation_sim_values, na.rm = T) # as expected # the mean is around the parameter I gave
```

df_long_for_metan <- df_long_for_metan %>%
  rowwise() %>%
  mutate(responders = sum(rnorm(baseline_n, post_mean, 
                                post_sd) < (baseline_mean/ 2)))

df_long_for_metan <- df_long_for_metan %>%
  rowwise() %>%
  mutate(resp_rate = responders/baseline_n)

summary_resp_rate <- df_long_for_metan %>%
  group_by(group) %>%
  summarise(mean_resp_rate = mean(resp_rate, na.rm = TRUE),
            sd_resp_rate = sd(resp_rate, na.rm = TRUE))

test_summary <- df_with_distinct_instruments %>% 
  group_by(psy_or_med) %>% 
  summarise(rr_active = mean(resp_rate_active, na.rm = TRUE),
            rr_control = mean(resp_rate_control, na.rm = TRUE),
            n = n())

@@

# Filter out wl conditions
df_descr_psy_conditions <- df_descr_psy_conditions %>% 
  filter(new_study_id %in% no_wl_ids)

# count_wl <- df_long_for_metan %>% 
#   filter(treatment == "wlc") %>% 
#   distinct(new_study_id) %>% 
#   nrow()
# 
# count_cau <- df_long_for_metan %>% 
#   filter(treatment == "cau") %>% 
#   distinct(new_study_id) %>% 
#   nrow()
